Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-03 manuscript.tex
20161104

However, there also exist some obstacles in the hybrid control design. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide the infinite propelling force~\cite{martinez1998spacecraft}. In simpler terms, the tension and thruster force for the tether deployment are both limited, and the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable. Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about input limitation of the TSS, providing many solutions on satellite arrangements and deployments. Huang et al. proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}. \textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par

>>>>

However, there also exist some obstacles in the hybrid control design. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the space tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the tether. Also, the thruster can not provide the infinite propelling force~\cite{martinez1998spacecraft}. In simpler terms, the tension and the thruster force for the deployment are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable. Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about input limitation of the TSS, providing many solutions on satellite arrangements and deployments. Huang et al. proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}. \textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
